Revisiting Multi-Domain Machine Translation

### 2020-09-02 2020/tacl2020/multidomain.tex
score of cluster groups

\begin{table*}[t]
\centering \footnotesize
\revision{
  \begin{tabular}{|p{1.3cm}|*{11}{c|}} \hline
   Model/ & Train &\system{Mixed}&\system{FT}&\system{FT}&\system{MDL}&\system{DC}&\system{DC}&\multirow{2}{*}{\system{TTM}}&\multirow{2}{*}{\system{ADM}}&\multirow{2}{*}{\system{DM}}&\multirow{2}{*}{\system{LDR}}  \\ 
   Clusters & size & \system{Nat} & \system{Full} & \system{Res} &\system{Res} & \system{Feat}& \system{Tag}& & & & \\ \hline
10 small&29.3k&60.2&60.7&62.6&62.7&\bf 63.6&47.3&62.1&61.3&58.8&62.5\\
10 mid&104.7k&40.6&\bf 42.6&41.9&41.2&40.9&38.3&40.2&39.5&36.9&40.5\\
10 large&251.1k&48.7&\bf 50.7&49.5&48.9&48.2&44.6&47.7&47.2&44.4&47.9\\
Avg& &128.4k&\bf 51.3&\bf 51.3&50.9&50.9&43.4&50.0&49.4&46.7&50.29 \\ \hline
  \end{tabular}
   \caption{BLEU scores computed by merging the 10 smaller, medium, and larger cluster test sets. Best score for each group is in boldface. For the small clusters, full-fine tuning is outperformed by several MDMT systems - see details in Appendix~B.}
   \label{tab:avg_automatic_domains}}
\end{table*}
Finally, Table~\ref{tab:subdomains} reports the effect of using automatic domain for each of the 6 test sets: each sentence was first assigned to an automatic class, translated with the corresponding multi-domain system with 30 classes; aggregate numbers were then computed, and contrasted with the 6-domain scenario. Results are clear and confirm previous observations: even though some clusters are very close, the net effect is a loss in performance for almost all systems and conditions. In this setting, the best MDMT in our pool (\system{MDL-Res}) is no longer able to surpass the \system{Mix-Nat} baseline.%\fyTodo{Note about scaling?}\fyTodo{More comparison?}

>>>>

\begin{table*}[t]
\centering \footnotesize
\revision{
  \begin{tabular}{|p{1.3cm}|*{11}{c|}} \hline
   Model/ & Train &\system{Mixed}&\system{FT}&\system{FT}&\system{MDL}&\system{DC}&\system{DC}&\multirow{2}{*}{\system{TTM}}&\multirow{2}{*}{\system{ADM}}&\multirow{2}{*}{\system{DM}}&\multirow{2}{*}{\system{LDR}}  \\ 
   Clusters & size & \system{Nat} & \system{Full} & \system{Res} &\system{Res} & \system{Feat}& \system{Tag}& & & & \\ \hline
10 small&29.3k&68.3&70.0&70.7&\bf 71.2&70.6&53.1&67.3&69.8&67.0&70.2\\
10 mid&104.7k&44.8&\bf 48.0&46.0&45.7&44.8&44.3&44.5&43.7&41.6&44.5\\
10 large&251.1k&50.4&\bf 52.9&52.0&51.3&49.6&43.2&49.1&48.5&44.3&49.5\\
Avg& &128.4k&\bf 51.3&\bf 51.3&50.9&50.9&43.4&50.0&49.4&46.7&50.29 \\ \hline
  \end{tabular}
   \caption{BLEU scores computed by merging the 10 smaller, medium, and larger cluster test sets. Best score for each group is in boldface. For the small clusters, full-fine tuning is outperformed by several MDMT systems - see details in Appendix~B.}
   \label{tab:avg_automatic_domains}}
\end{table*}
Finally, Table~\ref{tab:subdomains} reports the effect of using automatic domain for each of the 6 test sets: each sentence was first assigned to an automatic class, translated with the corresponding multi-domain system with 30 classes; aggregate numbers were then computed, and contrasted with the 6-domain scenario. Results are clear and confirm previous observations: even though some clusters are very close, the net effect is a loss in performance for almost all systems and conditions. In this setting, the best MDMT in our pool (\system{MDL-Res}) is no longer able to surpass the \system{Mix-Nat} baseline.%\fyTodo{Note about scaling?}\fyTodo{More comparison?}
